### 2021-05-15 geography/ia/paper.tex
bipolar semantic survey tallies + charts etc

The fieldwork for our paper was conducted in Paris, one of the largest and most well known cities in the world. The city itself is arranged in a manner such that 20 districts, known locally as \textit{arrondissements}, are placed in a spiral in the city. It is globally known for its high number of tourists per year, equating to around 35 million tourists in the year 2019 alone. \footcite{statista_department_27_2020} Many of them come to visit the world-renowned Eiffel Tower, located in the VII\textsuperscript{th} \textit{arrondissement}. \footcite{condor_ferries} To add, Paris is home to 2.2 million people, who mostly live in the outer residential areas, from the XI\textsuperscript{th} to the XX\textsuperscript{th} \textit{arrondissements}.

@@

\subsection{Our sampling method}

The sites in the two areas were chosen using a method of stratified sampling, as seeing that the VVI\textsuperscript{th} does indeed contain residential sites and the XVI\textsuperscript{th} touristic ones, we can discard the ones that are irrelevant to our study.

@@

The sites will be visited to conduct a so-called "bipolar survey", which consists of rating the site based on multiple criteria. This process was done by selecting a single person from our group to visit one of the sites, and complete a bipolar semantic survey. They would grade several different aspects of the site (such as general cleanliness, noise, amount of cars), and take a set of 3 images of the site.\footnote{Images taken for our study can be found at \url{https://github.com/kinnounko/notes/tree/main/geography/ia/images}}

@@

\subsection{Appendix Test}
\label{app:test}

>>>>

In order to answer this question, the fieldwork for our paper was conducted in Paris, one of the largest and most well known cities in the world. The city itself is arranged in a manner such that 20 districts, known locally as \textit{arrondissements}, are placed in a spiral in the city. It is globally known for its high number of tourists per year, equating to around 35 million tourists in the year 2019 alone. \footcite{statista_department_27_2020} Many of them come to visit the world-renowned Eiffel Tower, located in the VII\textsuperscript{th} \textit{arrondissement}. \footcite{condor_ferries} To add, Paris is home to 2.2 million people, who mostly live in the outer residential areas, from the XI\textsuperscript{th} to the XX\textsuperscript{th} \textit{arrondissements}.

@@

\subsubsection{Our sampling method}

The sites in the two areas were chosen using a method of stratified sampling, as seeing that the VII\textsuperscript{th} does indeed contain residential sites and the XVI\textsuperscript{th} touristic ones, we can discard the ones that are irrelevant to our study.

@@

The sites will be visited to conduct a so-called "bipolar survey", which consists of rating the site based on multiple criteria. This process was done by selecting a single person from our group to visit one of the sites, and complete a bipolar semantic survey. They would grade several different aspects of the site (such as general cleanliness, noise, amount of cars), and take a set of 3 images of the site.\footnote{Images taken for our study can be found at \url{https://github.com/kinnounko/notes/tree/main/geography/ia/images}} Our surveys were conducted during the week of the 10th of March, 2021 in the afternoon each time. The weather was overcast and moderately cold.

Our results for the bipolar survey are shown in Appendix \ref{app:bipolar}

When tallied, the total scores for each site can be expressed as a fraction over 84, as shown in Figures 5, 6.

\begin{figure}
    \begin{center}
        \begin{tabular}{||c c||}
            \hline
            Site & Total score  \\ [0.5ex]
            \hline\hline
            Bir-Hakeim                 & 51    \\
            \hline
            Seine river bank           & 69    \\
            \hline
            Foot of the Eiffel Tower   & 45    \\
            \hline
            Iena Bridge                & 42    \\
            \hline
            Ecole Militaire            & 54    \\ [1ex]
            \hline
        \end{tabular}
    \end{center}
    \caption{Total Bipolar Semantic scores for the VII\textsuperscript{th}}
\end{figure}

\begin{figure}
    \begin{center}
        \begin{tabular}{||c c||}
            \hline
            Site & Total score  \\ [0.5ex]
            \hline\hline
            Rue Davioud 1       & 47    \\
            \hline
            Rue Davioud 2       & 53    \\
            \hline
            Avenue Mozart       & 31    \\
            \hline
            Avenue Paul Doumer  & 35    \\
            \hline
            Ranelagh Garden     & 77    \\ [1ex]
            \hline
        \end{tabular}
    \end{center}
    \caption{Total Bipolar Semantic scores for the XVI\textsuperscript{th}}
\end{figure}

When plotted on a map, these totals can be shown with a gradient of colors.

@@

\subsection{Bipolar survey results}
\label{app:bipolar}

Shown below are our results from our bipolar semantic survey:

XVI\textsuperscript{th} residential area:

\includegraphics[width=0.5\linewidth]{media/bipolar/mozart.png}
\includegraphics[width=0.5\linewidth]{media/bipolar/davioud1.png}
\includegraphics[width=0.5\linewidth]{media/bipolar/davioud2.png}
\includegraphics[width=0.5\linewidth]{media/bipolar/ranelagh.png}
\includegraphics[width=0.5\linewidth]{media/bipolar/pauldoumer.png}

VII\textsuperscript{th} touristic area:

\includegraphics[width=0.5\linewidth]{media/bipolar/birhakeim.png}
\includegraphics[width=0.5\linewidth]{media/bipolar/ecolemilitaire.png}
\includegraphics[width=0.5\linewidth]{media/bipolar/eiffel.png}
\includegraphics[width=0.5\linewidth]{media/bipolar/iena.png}
\includegraphics[width=0.5\linewidth]{media/bipolar/seinebank.png}
